\documentclass[a4paper]{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{textcomp}
\usepackage{fontawesome5}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{hyperref}
\textheight=10in
\pagestyle{empty}
\raggedright

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex}

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\area} [2] {
	\vspace*{-9pt}
	\begin{verse}
		\textbf{#1}   #2
	\end{verse}
}
\newcommand{\lineunder} {
	\vspace*{-8pt} \\
	\hspace*{-18pt} \hrulefill \\
}
\newcommand{\header} [1] {
	{\hspace*{-18pt}\vspace*{6pt} \textcolor{Cerulean}{\textsc{#1}}}
	\vspace*{-6pt} \textcolor{Cerulean}{\lineunder}
}
\newcommand{\subheader} [1] {
	{\hspace*{-9pt}\vspace*{6pt} \textcolor{Cerulean}{\textsc{#1}}}
	\vspace*{-6pt}
}
\newcommand{\employer} [3] {
	{ \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}
\newcommand{\contact} [3] {
	\vspace*{-10pt}
	\begin{center}
		{\Huge \scshape {#1}}\\
		#2 \\ #3
	\end{center}
	\vspace*{-8pt}
}


\begin{document}
\vspace*{-40pt}
\vspace*{-10pt}
\begin{center}
{\Huge \scshape {Christian A. Stratton}} \\
\faMapMarker \ Bozeman, MT, 59715 \\
\faEnvelope \ \href{mailto:christianstratton@montana.edu}{christianstratton@montana.edu} \\ 
\faGlobe \ \href{https://christianstratton.github.io/}{https://christianstratton.github.io/} \\
\faPhone \ (406) 261-9426 \\ 
\end{center}
\vspace*{2mm}

\header{Summary}
\vspace*{2mm}

Assistant professor of statistics with consulting, research, and
teaching experience. Strong analytical skills pertaining to spatial
statistics, Bayesian computation, and analysis of ecological data types.
Research interests include: Bayesian computation, spatial statistics,
species distribution modeling, modeling of wildlife disease, data
visualization, and teaching techniques for data science.

\vspace*{2mm}
\header{Education}
\vspace*{2mm}

\textbf{Montana State University}\hfill Bozeman, MT

Doctor of Philosophy in Statistics \hfill May 2022

Dissertation:
\textit{Bayesian Hierarchical Latent Variable Models for Ecological Data Types}

Advisors: Dr.~Andrew Hoegh and Dr.~Jennifer Green

\vspace{2mm}

\textbf{Montana State University} \hfill Bozeman, MT

Master of Science in Statistics \hfill May 2018

\vspace{2mm}

\textbf{Montana State University} \hfill Bozeman, MT

Bachelor of Science with Honors in Mathematics (focus: Statistics)
\hfill December 2016

\vspace{2mm}

\header{Peer-reviewed Journal Articles}
\vspace*{2mm}

\subheader{Published}
\vspace*{2mm}

\textbf{10) Stratton, C.}, A. Hoegh, T.J. Rodhouse, J.L. Green, K.M.
Banner, K.M. Irvine.
2024.\href{https://doi.org/10.1111/2041-210X.14389}{Clustering and
unconstrained ordination with Dirichlet process mixture models.}
\textit{Methods in Ecology and Evolution}. \vspace*{2mm}

\textbf{9) Stratton, C.} K.M Irvine, K.M. Banner, E.S. Almberg, D.
Bachen, and K. Smucker. 2024.
\href{https://doi.org/10.1007/s13253-023-00593-8}{``Joint spatial
modeling bridges the gap between disparate disease surveillance and
population monitoring efforts informing conservation of at-risk bat
species.''}.
\textit{Journal of Agricultural, Biological, and Environmental Statistics}.
\vspace*{2mm}

\textbf{8) Stratton, C.}, K.M. Irvine, K.M. Banner, W.J. Wright, C.
Lausen, J. Rae. 2022.
\href{https://doi.org/10.1111/2041-210X.13831}{``Coupling validation
effort with \emph{in situ} bioacoustic data improves estimating relative
activity and occupancy for multiple species with cross-species
misclassifications.''} \textit{Methods in Ecology and Evolution}, 13(6),
p.~1288 -- 1303. \vspace*{2mm}

\textbf{7)} Khalighifar, A., B.S. Gotthold, E. Adams, J. Barnett, L.O.
Beard, E.R. Britzke, P.A. Burger, K. Chase, Z. Cordes, P.M. Cryan, E.
Ferrall, C.T. Fill, S.E. Gibson, G.S. Haulton, K.M. Irvine, L.S. Katz,
W.L. Kendall, C.A. Long, O.M. Aodha, T. McBurney, S. McCarthy, M.W.
McKown, J. O'Keefe, L.D. Patterson, K.A. Pitcher, M. Rustand, J.L.
Segers, K. Seppanen, J.L. Simers, \textbf{C. Stratton}, B.R. Straw, T.J.
Weller, and B.E. Reichert. 2022.
\href{https://doi.org/10.1111/1365-2664.14280}{``\emph{NABat ML}:
Utilizing deep learning to enable crowdsourced development of automated,
scalable solutions for documenting North American bat populations.''}
\textit{Journal of Applied Ecology}, 56(11), p.~2849 -- 2862.
\vspace*{2mm}

\textbf{6)} Irvine, K.M., K.M. Banner, \textbf{C. Stratton}, W.M. Ford,
and B.E. Reichert. 2022.
\href{https://doi.org/10.1002/ecs2.4142}{``Statistical assessment on
determining local presence of rare bat species.''} \textit{Ecosphere},
13(6), p.~e4142. \vspace*{2mm}

\textbf{5) Stratton, C.}, J.L. Green, and A. Hoegh. 2021.
\href{https://doi.org/10.5070/T513146468}{``Not just normal: Exploring
power with Shiny apps.''}
\textit{Technology Innovations in Statistics Education}, 13(1), p.~1 --
37. \vspace*{2mm}

\textbf{4)} Sepulveda, A.J., A. Hoegh, J.A. Gage, S.L Caldwell-Eldridge,
J.M. Birch, \textbf{C. Stratton}, P.R. Hutchins, E.P. Barnhart. 2021.
\href{https://doi.org/10.3389/fevo.2021.620715}{``Integrating
environmental DNA results with diverse data sets to improve
biosurveillance of river health.''}
\textit{Frontiers in Ecology and Evolution}, 9, p.~1 -- 13.
\vspace*{2mm}

\textbf{3) Stratton, C.}, A.J. Sepulveda, and A. Hoegh. 2020.
\href{https://doi.org/10.1111/2041-210X.13442}{``\texttt{msocc:} Fit and
analyze computationally efficient multi-scale occupancy models in
\texttt{R}.''} \textit{Methods in Ecology and Evolution}, 11(9), p.~1113
-- 1120. \vspace*{2mm}

\textbf{2)} Sepulveda, A. J., C. Schmidt, J. Amberg, P. Hutchins,
\textbf{C. Stratton}, C. Mebane, M. B. Laramie, and D. S. Pilliod. 2019.
\href{https://doi.org/10.1002/ecs2.2843}{``Adding invasive species
biosurveillance to the U.S. Geological Survey streamgage network.''}
\textit{Ecosphere}, 10(8), p.~1 -- 17. \vspace*{2mm}

\textbf{1)} Hoegh, A., K. Flagg, and \textbf{C. Stratton}. 2018.
Contributed comment on Article by Bradley, Holan, and Wikle
\href{https://eds.p.ebscohost.com/abstract?site=eds&scope=site&jrnl=19360975&AN=138950462&h=fupOc1pyeH8dv67mdPoRzhYvo96LS\%2bzCYNHIjAcMPojnVBydkua\%2fXFU6RanU78MDh8WNMlzPVI\%2fBxvaUiWvg\%2bw\%3d\%3d&crl=c&resultLocal=ErrCrlNoResults&resultNs=Ehost&crlhashurl=login.aspx\%3fdirect\%3dtrue\%26profile\%3dehost\%26scope\%3dsite\%26authtype\%3dcrawler\%26jrnl\%3d19360975\%26AN\%3d138950462}{Invited
commentary on ``Computationally efficient multivariate spatio-temporal
models for high-dimensional count-valued data'' by Jonathan R. Bradley,
Scott H. Holan, and Christopher K. Wikle.}
\textit{Bayesian Data Analysis}, 13(1), p.~253 -- 310. \vspace*{2mm}

\subheader{In Review}
\vspace*{2mm}

Oram, J., K.M. Banner, \textbf{Stratton, C.}, Andrew Hoegh, and K.M.
Irvine. ``Leveraging the observed-data likelihood improves using machine
learning labels in a Bayesian hierarchical model for bioacoustic data.''
In review in \textit{Annals of Applied Statistics.} \vspace*{2mm}

\header{Peer-reviewed Technical Reports}
\vspace*{2mm}

\textbf{8) Stratton, C.}, K.M. Banner, and K.M. Irvine. 2023.
\href{https://code.usgs.gov/usgs/norock/irvine_k/spatial-misalignment-application}{``Code
vignette for application of the spatially misaligned regression model
described in `Joint spatial modeling bridges the gap between disparate
disease surveillance and population monitoring efforts informing
conservation of at-risk bat species,' U.S. Geological Survey software
release''} \vspace*{2mm}

\textbf{7)} Udell, B.J., \textbf{C. Stratton}, B.R. Straw, K.M. Irvine,
J.D. Reichard, S.M. Gaulke, J.T.H. Coleman, F. Tousley, R.D. Inman, A.N.
Schuhmann, R. Shively, and B.E. Reichert. 2023.
\href{https://doi.org/10.5066/P9MV37I7}{``North American Bat Monitoring
Program (NABat) Integrated Summer Species Distribution Model: Predicted
Tricolored Bat Occupancy Probabilities: U.S. Geological Survey data
release.''} \vspace*{2mm}

\textbf{6) Stratton, C.}, B.R. Straw, J.H. Cox, K.M. Irvine, F.C.
Tousley, and B.E. Reichert. 2023.
\href{https://doi.org/10.5066/P9H8NEOY}{``Attributed North American
Grid-Based Offshore Sampling Frames: U.S. Geological Survey data
release.''} \vspace*{2mm}

\textbf{5) Stratton, C.}, K.M. Irvine. 2022. Summertime analysis
statistical report for Little Brown, Northern Long-eared, and Tricolored
bat species status assessment. Chapter B in Straw, B.R, J. A. Martin,
J.D Reichard, and B.E Reichert, editors.
\href{https://doi.org/10.7944/P9B4RWEU}{``Analytical assessments in
support of the U.S. Fish and Wildlife Service 3-Bat species status
assessment. Cooperator report prepared in cooperation with the U.S.
Geological Survey, United States Fish and Wildlife Service and Bat
Conservation International.''} \vspace*{2mm}

\textbf{4)} Udell, B.J., B.R. Straw, T.L. Cheng, K. Enns, W.F. Frick, B.
Gotthold, K.M. Irvine, C. Lausen, S. Loeb, J.D. Reichard, T.J. Rodhouse,
D. Smith, \textbf{C. Stratton}, W.E. Thogmartin, and B.E. Reichert.
2022. \href{https://doi.org/10.5066/P92JGACB}{``Status and trends of
North American bats: Summer occupancy analysis 2010-2019.''} U.S. Fish
and Wildlife Service. \vspace*{2mm}

\textbf{3)} Irvine, K.M., and \textbf{C. Stratton}. 2021.
\href{https://doi.org/10.5066/P9XZ8D6N.}{``Rangewide summertime model
predictions for three bat species (\textit{Myotis lucifigus},
\textit{Myotis septentrionalis}, and \textit{Perimyotis subflavus}) from
acoustic and mist net data 2010 to 2019: US Geological Survey data
release.''} \vspace*{2mm}

\textbf{2)} Wessel, S.A., L. Jones, E. Kramer, \textbf{C. Stratton}, L.
Shoemaker, and D. Laughlin. 2020.
\href{https://journals.uwyo.edu/index.php/uwnpsrc/article/view/6791/6301}{``Predictability
and stability of sagebrush-steppe restoration in a changing climate.''}
National Park Service Annual Report Vol. 43. \vspace*{2mm}

\textbf{1) Stratton, C.}, A. Hoegh, K. M. Irvine, K. Legg, K. McCloskey,
E. Shanahan, M. Tercek, and D. Thoma. 2019.
\href{https://irma.nps.gov/DataStore/DownloadFile/631136}{``Assessing
spatial and temporal patterns in sagebrush steppe vegetation
communities, 2012-2018: Grand Teton National Park.''} Natural Resource
Report NPS/GRYN/NRR-2019/2020. National Park Service, Fort Collins,
Colorado. \vspace*{2mm}

\header{Presentations}
\vspace*{2mm}

\textbf{11) Stratton, C.}, K.M. Irvine, K.M. Banner, E. Almberg, D.
Bachen, and K. Smucker. September 2023. ``Joint spatial modeling bridges
the gap between disparate disease surveillance and population monitoring
efforts informing conservation of at-risk bat species'' Invited talk
given at the MT Chapter of the ASA annual meeting. Bozeman, MT, USA.
\vspace*{2mm}

\textbf{10) Stratton, C.}, K.M. Irvine, K.M. Banner, E. Almberg, D.
Bachen, and K. Smucker. August 2023. ``Joint spatial modeling of
ecological response and disease processes improves estimator
precision.'' Talk given at the Joint Statistical Meetings. Toronto,
Ontario, Canada. \vspace*{2mm}

\textbf{9) Stratton, C.}, K.M. Irvine, K.M. Banner, E. Almberg, D.
Bachen, and K. Smucker. June 2023. ``A statistical framework for
integrating White-nose syndrome surveillance data and acoustic
population monitoring data.'' Talk given to the U.S. Geological Survey
Disease Coordination Group. Virtual. \vspace*{2mm}

\textbf{8) Stratton, C.}, K.M. Irvine, K.M. Banner, E. Almberg, D.
Bachen, and K. Smucker. June 2023. ``Leveraging WNS surveillance and
NABat data improves estimation of disease spread and bat activity.''
Poster presented at the Whitenose Syndrome National Meeting. Palm
Springs, California, USA. \vspace*{2mm}

\textbf{7) Stratton, C.}, K.M. Irvine, E. Almberg, K. Smucker, and J.
Gude. October 2022. ``Joint spatial modeling of relative activity and
disease processes.'' Poster presented at the ENVR 2022 Workshop:
Environmental and Ecological Statistical Research and Applications with
Societal Impacts. Provo, Utah, USA. \vspace*{2mm}

\textbf{6) Stratton, C.}, K.M. Irvine, E. Almberg, K. Smucker, and J.
Gude. October 2022. ``Bats \& Stats: Assessing Impacts of White-nose
Syndrome on Western Bat Species.'' Talk given at the Northern Rocky
Mountain Science Center. Bozeman, Montana, USA. \vspace*{2mm}

\textbf{5) Stratton, C.}, A. Hoegh, K.M. Irvine, K.M. Banner. August
2021. ``Clustering and ordination with Dirichlet process mixture
models.'' Invited talk given at the Joint Statistical Meetings. Virtual.
\vspace*{2mm}

\textbf{4) Stratton, C.}, J.L. Green. June 2021. ``Beyond normal:
Understanding power through \texttt{R} Shiny.'' Poster presented at the
United States Conference on Teaching Statistics. Virtual. \vspace*{2mm}

\textbf{3) Stratton, C.}, A. Hoegh, and J.L. Green. August 2018.
``Predicting pitch type: A case study in Bayesian hierarchical
multinomial regression.'' Invited talk given at the Joint Statistical
Meetings. Vancouver, Canada. \vspace*{2mm}

\textbf{2) Stratton, C.}, A. Hoegh, and J.L. Green. August 2018.
``Unraveling Kershaw's dominance.'' Poster presented at The Cascadia
Symposium on Statistics in Sports. Vancouver, Canada. \vspace*{2mm}

\textbf{1) Stratton, C.} and J.L. Green. May 2018. ``The power of
technology: A Shiny applet assisted approach to teaching statistical
power.'' Poster presented at the Electronic Conference on Teaching
Statistics. Virtual. \vspace*{2mm}

\header{Peer-reviewed Science Software}
\vspace*{2mm}

\textbf{Stratton, C.}, A. Hoegh, A. Sepulveda, and K.M. Banner. 2020.
``\texttt{msocc}.'' \texttt{R} package to support computationally
efficient implementation of Bayesian multi-scale occupancy models.
\vspace*{2mm}

\header{Research and Collaboration Experience}
\vspace*{2mm}

\textbf{Middlebury College} \hfill Middlebury, VT

\textit{Assistant Professor of Statistics} \hfill July 2024 - Present

\vspace{-1mm}
\begin{itemize} \itemsep 1pt
    \item Developed new courses in statistics
    \item Mentored and advised undergraduate students
    \item Led collaborative research projects with faculty and students
\end{itemize}

\textbf{Montana State University} \hfill Bozeman, MT

\textit{Post-doctoral researcher} \hfill July 2022 - May 2024

Advisors: Dr.~Kathryn Irvine (USGS) and Dr.~Katharine Banner (MSU)

\vspace{-1mm}
\begin{itemize} \itemsep 1pt
    \item Developed statistical modeling frameworks for ecological data structures
    \item Authored multiple peer-reviewed journal articles and technical reports
    \item Communicated complicated statistical models to domain experts from multiple agencies
    \item Co-mentored a graduate-level statistician in support of research and analyses
\end{itemize}

\textbf{U.S. Geological Survey} \hfill Bozeman, MT

\textit{Student contractor} \hfill August 2020 - July 2022

Supervisor: Dr.~Kathryn Irvine (USGS)

\vspace{-1mm}
\begin{itemize} \itemsep 1pt
   \item Provided analyses for Endangered Species Act listing decisions
   \item Authored peer-review journal articles and technical reports
   \item Collaborated with scientists from multiple domains 
\end{itemize}

\textbf{Montana State University} \hfill Bozeman, MT

\textit{Graduate Research Assistant} \hfill January 2019 - August 2020

\vspace{-1mm}
\begin{itemize} \itemsep 1pt
   \item Resolved a wide scope of ecological problems using various techniques
   \item Collaborated and communicated with domain experts in ecology and land-resource management
   \item Developed models and tools to aid collaborators
   \item Authored papers, web applications, and R packages
\end{itemize}

\textbf{Montana State University} \hfill Bozeman, MT

\textit{Statistical Consultant} \hfill August 2017 - May 2018

\vspace{-1mm}
\begin{itemize} \itemsep 1pt
   \item Communicated with clients
   \item Identified solutions to a wide scope of problems
   \item Successfully collaborated across departments to resolve problems
\end{itemize}

\header{Teaching Experience}
\vspace*{2mm}

\textbf{Instructor of Record} \hfill Middlebury, VT

\emph{STAT 0311: Statistical Inference} \hfill S25

Lead instructor responsibilities included: developing course materials,
facilitating active learning environments, holding office hours for
students. \vspace*{2mm}

\textbf{Instructor of Record} \hfill Middlebury, VT

\emph{STAT 0116: Introduction to Statistical Science} \hfill S25

Lead instructor responsibilities included: developing course materials,
facilitating active learning environments, holding office hours for
students. \vspace*{2mm}

\textbf{Instructor of Record} \hfill Middlebury, VT

\emph{STAT 0219: Time Series Analysis} \hfill F24

Lead instructor responsibilities included: developing course materials,
facilitating active learning environments, holding office hours for
students. \vspace*{2mm}

\textbf{Instructor of Record} \hfill Middlebury, VT

\emph{STAT 0116: Introduction to Statistical Science} \hfill F24

Lead instructor responsibilities included: developing course materials,
facilitating active learning environments, holding office hours for
students. \vspace*{2mm}

\textbf{Guest Lecturer} \hfill Bozeman, MT

\emph{STAT 408: Statistical Computing and Graphics Analysis} \hfill S22

Provided guest lectures on data visualization with the
\texttt{tidyverse} and implementing version control software in
statistical analyses to undergraduate-level statistics students.
\vspace*{2mm}

\textbf{Supervisor} \hfill Bozeman, MT

\emph{Math and Stat Learning Center} \hfill F19

Supervised undergraduate and graduate tutors in the Mathematics and
Statistics Learning Center. Responsibilities included coordinating
monthly meeting, proposing and implementing logistical improvements,
instructing tutors on how to effectively communicate mathematics and
statistics, and tutoring undergraduate students in a variety of courses,
including Calculus I-III, Linear Algebra, Introduction to Statistics,
and Intermediate Statistical Concepts.\vspace*{2mm}

\textbf{Guest Lecturer} \hfill Bozeman, MT

\emph{STAT 402/502: Intermediate Mathematical Statistics} \hfill S19

Provided guest lecture on interpreting statistical power to
undergraduate-level and graduate-level mathematical statistics students
using \texttt{R\ Shiny}. \vspace*{2mm}

\textbf{Graduate Teaching Assistant} \hfill Bozeman, MT

\emph{STAT 411/511: Methods for Data Analysis I} \hfill S19

Teaching assistant responsibilities included: grading homeworks and
exams, writing and leading interactive lab assignments, and providing
intermittent lectures on coding in \texttt{R} with an emphasis on data
visualization. \vspace*{2mm}

\textbf{Instructor of Record} \hfill Bozeman, MT

\emph{STAT 217: Intermediate Statistical Concepts} \hfill F18

Lead instructor responsibilities included: leading lectures, writing
lecture notes, writing and grading homeworks and exams, writing lab
assignments, and supervising teaching assistants. \vspace*{2mm}

\textbf{Instructor of Record} \hfill Bozeman, MT

\emph{STAT 216: Introduction to Statistics} \hfill S17, F17, S18

Lead instructor responsibilities included: implementing active learning
teaching strategies in class, planning and preparing course materials,
holding office hours for students. \vspace*{2mm}

\textbf{Undergraduate Teaching Assistant} \hfill Bozeman, MT

\emph{STAT 216: Introduction to Statistics} \hfill F15, S16, F16

Teaching responsibilities included: facilitating discussion during
in-class activities and holding office hours for students. \vspace*{2mm}

\textbf{Tutor} \hfill Bozeman, MT

\emph{Math and Stat Learning Center} \hfill F14, S15, F15, S16, F16

Tutored undergraduate students in the Mathematics and Statistics
Learning Center in a wide variety of courses, including: College
Algebra, Calculus I-III, Linear Algebra, Introduction to Statistics, and
Intermediate Statistical Concepts.\vspace*{2mm}

\header{Service}

\textbf{Montana Chapter of the American Statistical Association}
\hfill Bozeman, MT

\emph{Chapter Secretary and Council of Chapters Representative}
\hfill Sept 2022 - Present

Responsibilities included facilitating coordination of annual meetings,
keeping meeting notes, and attending the Council of Chapters session at
the Joint Statistical Meetings. \vspace*{2mm}

\textbf{Bozeman Environmental and Ecological Statistics (BEES)}
\hfill Bozeman, MT

\emph{Co-President} \hfill Sept 2022 - Present

The BEES research group is a group focused on mentoring graduate
students with interest in statistical research motivated by
environmental and ecological applications. Responsibilities as
co-president include coordinating bi-weekly meetings, mentoring graduate
students, providing papers for literature review sessions, maintaining
the group website, and coordinating invited speaker presentations.
\vspace*{2mm}

\textbf{Annals of Applied Statistics}

\emph{Referee} \hfill 2023

Refereed papers for the \emph{Annals of Applied Statistics} journal.
\vspace*{2mm}

\textbf{Montana State University STEAM Day} \hfill Bozeman, MT

\emph{Workshop Presenter} \hfill April 2023

MSU STEAM Day is a one-day conference that includes hands-on workshops
in the STEAM fields of science, technology, engineering, art and math
for girls in grades six, seven, and eight. Responsibilities included
presenting an interactive activity introducing statistical inference
using the dice game Pass the Pigs. \vspace*{2mm}

\textbf{DataFest} \hfill Bozeman, MT

\emph{Volunteer judge} \hfill April 2019, April 2022

Volunteer responsibilities included providing guidance to
undergraduate-level and graduate-level students competing in DataFest
competition. \vspace*{2mm}

\header{Awards}
\vspace*{2mm}

\textbf{Three Minute Thesis Competition Finalist} \hfill Bozeman, MT

Finalist for the Three Minute Thesis competition \hfill February 2020

\vspace*{2mm}

\textbf{Dr. William A. Stannard Award for Excellence} \hfill Bozeman, MT

Recognition of outstanding graduate student teaching \hfill May 2018

\vspace*{2mm}

\textbf{Outstanding Graduate Student Award} \hfill Bozeman, MT

Recognition of superior academic achievement among graduate students
\hfill May 2017

\vspace*{2mm}

\textbf{John L. Magaret Math/Science Scholarship} \hfill Bozeman, MT

Recipient of scholarship for outstanding academic achievement
\hfill January 2017

\vspace*{2mm}

\textbf{Milton-Chauner Math Scholarship} \hfill Bozeman, MT

Recipient of scholarship for outstanding academic achievement
\hfill August 2016

\vspace*{2mm}

\textbf{Outstanding Undergraduate Student Award} \hfill Bozeman, MT

Recognition of superior academic achievement among undergraduate
students \hfill May 2016

\vspace*{2mm}

\textbf{Outstanding Scholar Award} \hfill Bozeman, MT

Recognition of superior academic performance \hfill May 2016

\vspace*{2mm}

\textbf{Montana State University System Award} \hfill Bozeman, MT

Scholarship for outstanding academic performance \hfill December 2015

\vspace*{2mm}

\textbf{Phi Kappa Phi} \hfill Bozeman, MT

Member of Phi Kappa Phi, a national multi-disciplinary honor society
\hfill March 2015

\vspace*{2mm}

\textbf{Pi Mu Epsilon} \hfill Bozeman, MT

Member of Pi Mu Epsilon, a national mathematics honor society
\hfill December 2014

\vspace*{2mm}

\header{Skills}
\vspace*{2mm}
\begin{tabular}{ l l }
  Statistical computing languages:  & R, Julia, SAS \\
    Other programming languages:         &  HTML, Markdown, Quarto, R Shiny, Tableau \\
  Probabilistic programming languages:         & BUGS, JAGS, NIMBLE, Stan \\
    Database management systems:         & SQL, SQLite, Microsoft Excel \\
    Operating systems:       & Windows, Mac OS \\
\end{tabular}
\vspace*{2mm}
\end{document}
